HTW E3

### 2024-03-16 Analysis/combo_test.qmd
update e1 and e2 dist models to use separate RF's. Re render.

---
title: "HTW All Exp Testing"
categories: [Analyses, R, Bayesian]
page-layout: full
toc: false
---

```{r}
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,knitr,ggpattern,ggh4x)
conflict_prefer_all("dplyr", quiet = TRUE)
options(scipen = 999)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model"), ~ source(here::here(paste0("Functions/", .x, ".R"))))

@@

```{r}
ltest|> group_by(id,condit) |> pivot_longer(c("dist","train_end"),names_to="var",values_to="value") |> 
  ggplot(aes(x=var,y=value, fill=condit)) + stat_bar + facet_wrap(~var)

# create quartiles for train_end
test |> group_by(condit,vb,fb,bandOrder) |>  filter(bandType=="Extrapolation") |>
  mutate(train_end_q = ntile(train_end,4)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    ggh4x::facet_wrap2(bandOrder~vb~fb) +
  labs(x="Band", y="Deviation From Target")

@@

>>>>

---
title: "HTW All Exp Testing"
categories: [Analyses, R, Bayesian]
page-layout: full
toc: false
code-fold: true
code-tools: true
---

```{r}
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr,kableExtra,ggh4x,ggpattern)

conflict_prefer_all("dplyr", quiet = TRUE)
options(scipen = 999)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model"), ~ source(here::here(paste0("Functions/", .x, ".R"))))

@@

@@

### Control for end of training performance
```{r}
#| fig-height: 10
#| fig-width: 11

test|> group_by(id,condit) |> pivot_longer(c("dist","train_end"),names_to="var",values_to="value") |> 
  ggplot(aes(x=var,y=value, fill=condit)) + stat_bar + facet_wrap(~var)

# create quartiles for train_end
test |> group_by(condit,vb,fb,bandOrder) |>  filter(bandType=="Extrapolation") |>
  mutate(train_end_q = ntile(train_end,4)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    ggh4x::facet_wrap2(bandOrder~vb~fb) +
  labs(x="quartile", y="Deviation From Target")

### dist ~ condit * fb * bandOrder * bandInt + (1 + bandInt | id)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * fb * bandOrder * bandInt + (1 + bandInt | id)
bmm_combo_testDistBand <- readRDS(paste0(here::here("data/model_cache","combo_testDistBand_RF_5k.rds")))

mted1 <- as.data.frame(describe_posterior(bmm_combo_testDistBand, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testDistBand$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testDistBand),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### vx ~ condit * fb * bandOrder * bandInt + (1 + bandInt | id)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# vx ~ condit * fb * bandOrder * bandInt + (1 + bandInt | id)
bmm_combo_testVxBand<- readRDS(paste0(here::here("data/model_cache","combo_testVxBand_RF_5K.rds")))

mted2 <- as.data.frame(describe_posterior(bmm_combo_testVxBand, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testVxBand$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testVxBand),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### dist ~ condit * bandType * bandOrder * fb + (1 + bandType | id)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * bandType * bandOrder * fb + (1 + bandType | id)
bmm_combo_testBT_dist<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeDistBt_test6__4_5000_0.93_12_Bt_test6_1537.rds")))

mted4 <- as.data.frame(describe_posterior(bmm_combo_testBT_dist, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted4) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted4 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT_dist$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT_dist),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### dist ~ condit * bandType * bandOrder * fb + (1 | id) + (1 | bandInt)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * bandType * bandOrder * fb + (1 | id) + (1 | bandInt)
bmm_combo_testBT_dist3<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeDistBand_test6_RF_2_2_8000_0.94_13_Band_test6_RF_21817.rds")))

mted7 <- as.data.frame(describe_posterior(bmm_combo_testBT_dist3, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted7) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted7 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT_dist3$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT_dist3),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### dist ~ condit * bandType * bandOrder * fb + (1 | id) + (1 | bandInt)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * bandType * bandOrder * fb + (1 | id) + (1 | bandInt)
bmm_combo_testBT_dist2<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeDistBand_test6_RF_2_4_5000_0.94_14_Band_test6_RF_25437.rds")))

mted5 <- as.data.frame(describe_posterior(bmm_combo_testBT_dist2, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted5) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted5 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT_dist2$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT_dist2),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### dist ~ condit * bandType * bandOrder * fb + (1 | id * bandInt)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * bandType * bandOrder * fb + (1 | id * bandInt)
bmm_combo_testBT_dist4<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeDistBt_test6_RF_int_2_8000_0.94_13_Bt_test6_RF_int4808.rds")))

mted9 <- as.data.frame(describe_posterior(bmm_combo_testBT_dist4, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted9) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted9 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT_dist4$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT_dist4),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### dist ~ condit * bandType * bandOrder * fb + bandInt + (1 | id)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# dist ~ condit * bandType * bandOrder * fb + (1 | id) + (1 | bandInt)
bmm_combo_testBT_dist3<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeDistBand_test6_fixBandInt_RF_1_4_5000_0.94_14_Band_test6_fixBandInt_RF_10858.rds")))

mted5 <- as.data.frame(describe_posterior(bmm_combo_testBT_dist3, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted5) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted5 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT_dist3$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT_dist3),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### vx ~ condit * bandType * bandOrder * fb + (1 + bandType | id)
```{r}
#| fig-height: 10
#| fig-width: 11
#| 
# vx ~ condit * bandType * bandOrder * fb + (1 + bandType | id)
bmm_combo_testBT<- readRDS(paste0(here::here("data/model_cache/brms","combo_TeVxBt_test6__4_5000_0.93_12_Bt_test6_3033.rds")))

mted3 <- as.data.frame(describe_posterior(bmm_combo_testBT, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE, caption=(bmm_combo_testBT$formula[1]))

ce_bmm1 <- plot(conditional_effects(bmm_combo_testBT),points=FALSE,plot=FALSE)
wrap_plots(ce_bmm1)

### 2024-03-16 Analysis/e1_test.qmd
update e1 and e2 dist models to use separate RF's. Re render.

---
title: "HTW E1 Testing"
categories: [Analyses, R, Bayesian]
---

```{r setup1, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

```{r}

# create quartiles for train_end
testE1 |> group_by(condit,vb) |> 
  mutate(train_end_q = ntile(train_end,6)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

@@

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"

@@

>>>>

---
title: "HTW E1 Testing"
categories: [Analyses, R, Bayesian]
page-layout: full
toc: false
code-fold: true
code-tools: true
---

```{r setup1, include=FALSE}
source(here::here("Functions", "packages.R"))
options(brms.backend="cmdstanr",mc.cores=4)

e1 <- readRDS(here("data/e1_08-21-23.rds")) 
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
testE1 <- test <-  e1 |> filter(expMode2 == "Test")

testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

nbins=5
trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))

nbins=5
trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.bandStage, breaks = seq(1, max(gt.bandStage),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(train_end = mean(dist))

trainE1 |> select(id,condit,Trial_Bin,trial,vb,bandInt,dist,vx,gt.bandStage) |> 
  group_by(id,condit,vb,Trial_Bin) |> 
  summarise(mean_dist=mean(dist),mean_vx=mean(vx),n=n())

testE1 <- testE1 |> left_join(trainE1_avg, by=c("id","condit"))

@@

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "E1. Training vs. Extrapolation"
#| 
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
    data=testE1, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

#bayestestR::describe_posterior(bmtd)

mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
# posterior_summary(bmtd,variable=r_bandInt_params)
# 
# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
# posterior_summary(bmtd,variable=r_bandInt_params)

mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)

cdted1 <- get_coef_details(bmtd, "conditVaried")
cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")

@@

*Testing.* To compare conditions in the testing stage, we first fit a model predicting deviation from the target band as a function of training condition and band type, with random intercepts for participants and bands. The model is shown in @tbl-e1-bmm-dist. The effect of training condition was not reliably different from 0 (β = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`). The extrapolation testing items had a significantly greater deviation than the interpolation band (β = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`). The interaction between training condition and band type was significant (β = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), with the varied group showing a greater deviation than the constant group in the extrapolation bands. See @fig-e1-test-dev2.

```{r}
#| label: fig-e1-test-dev2
#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

(pe1td + pe1ce) + plot_annotation(tag_levels= 'A')

```{r}
#| label: tbl-e1-bmm-dist2
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"

@@

### control for training end performance

```{r}
#| fig-height: 9
#| fig-width: 10

# create quartiles for train_end
testE1 |> group_by(condit,vb) |> 
  mutate(train_end_q = ntile(train_end,6)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    facet_wrap(~vb) +
  labs(x="quartile", y="Deviation From Target")

```{r}
#| fig-height: 9
#| fig-width: 10
bmtd3 <- brm(dist ~ condit * bandType * train_end + (1|bandInt) + (1|id), 
    data=testE1, 
    file=paste0(here::here("data/model_cache","e1_trainEnd_BT_RF2")),
    iter=1000,chains=2, control = list(adapt_delta = .92, max_treedepth = 11))
summary(bmtd3)
bayestestR::describe_posterior(bmtd3)

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

 bmtd3 |> emmeans( ~condit * bandType * train_end) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
wrap_plots(ce_bmtd3)

### 2024-03-16 Analysis/e2.qmd
update e1 and e2 dist models to use separate RF's. Re render.

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RFint")
bmtd2 <- brm(dist ~ condit * bandType + (1|id*bandInt), 
    data=testE2, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

@@

mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |>
  kable(escape=F,booktabs=T) %>% kable_styling(font_size=8)

>>>>

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
    data=testE2, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

@@

mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |>
  kable(booktabs=TRUE)

### 2024-03-16 Analysis/e2_test.qmd
update e1 and e2 dist models to use separate RF's. Re render.

---
title: "HTW E2 Testing"
categories: [Analyses, R, Bayesian]
---

```{r setup2b, include=FALSE}
source(here::here("Functions", "packages.R"))
testE2 <- readRDS(here("data/e2_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

@@

@@

>>>>

---
title: "HTW E2 Testing"
categories: [Analyses, R, Bayesian]
page-layout: full
toc: false
code-fold: true
code-tools: true
---

```{r setup2b, include=FALSE}
source(here::here("Functions", "packages.R"))
options(brms.backend="cmdstanr",mc.cores=4)

e2 <- readRDS(here("data/e2_08-04-23.rds")) 
testE2 <- e2 |> filter(expMode2=="Test")
e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

nbins=5
trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
trainE2_avg <- trainE2_max |> group_by(id,condit) |> summarise(avg = mean(dist))

nbins=5
trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.bandStage, breaks = seq(1, max(gt.bandStage),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
trainE2_avg <- trainE2_max |> group_by(id,condit) |> summarise(train_end = mean(dist))

trainE2 |> select(id,condit,Trial_Bin,trial,vb,bandInt,dist,vx,gt.bandStage) |> 
  group_by(id,condit,vb,Trial_Bin) |> 
  summarise(mean_dist=mean(dist),mean_vx=mean(vx),n=n())

testE2 <- testE2 |> left_join(trainE2_avg, by=c("id","condit"))

@@

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
    data=testE2, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

#bayestestR::describe_posterior(bmtd)

mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |>
  kable(booktabs=TRUE)

```{r}
#| label: fig-e2-test-dev2
#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
pe1td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

pe1ce <- bmtd2 |> emmeans( ~condit + bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

(pe1td + pe1ce) + plot_annotation(tag_levels= 'A')

@@

condEffects <- function(m){
  m |> ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
    stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
    stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
    ylab("Predicted X Velocity") + xlab("Band")
}

@@

### control for training end performance

```{r}
#| fig-height: 9
#| fig-width: 10

testE2 |> group_by(id,condit) |> pivot_longer(c("dist","train_end"),names_to="var",values_to="value") |> 
  ggplot(aes(x=var,y=value, fill=condit)) + stat_bar + facet_wrap(~var)

testE2 |> ggplot(aes(x=train_end,y=dist,fill=condit)) + 
  stat_summary(geom = "line", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

testE2 |> ggplot(aes(x=train_end,y=dist,fill=condit,col=condit)) + 
  #geom_point() +
  geom_smooth(method="loess") +
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

# create quartiles for train_end
testE2 |> group_by(condit,vb) |> 
  mutate(train_end_q = ntile(train_end,4)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    facet_wrap(~vb) +
  labs(x="quartile", y="Deviation From Target")

```{r}
#| fig-height: 9
#| fig-width: 10
#| 
bmtd3 <- brm(dist ~ condit * bandType * train_end + (1|bandInt) + (1|id), 
    data=testE2, 
    file=paste0(here::here("data/model_cache","e2_trainEnd_BT_RF2")),
    iter=1000,chains=2, control = list(adapt_delta = .92, max_treedepth = 11))
summary(bmtd3)
bayestestR::describe_posterior(bmtd3)

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

 bmtd3 |> emmeans( ~condit * bandType * train_end) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
wrap_plots(ce_bmtd3)

### 2024-03-16 Analysis/e3.qmd
update e1 and e2 dist models to use separate RF's. Re render.

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RFint")
bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|id*bandInt), 
    data=testE3, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

@@

mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |>
  kable(escape=F,booktabs=T) %>% kable_styling(font_size=8)

@@

e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e3_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands") %>% kable_styling(font_size=8)

>>>>

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
    data=testE3, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

@@

mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |> 
  mutate(Term = stringr::str_remove(Term, "b_")) |>
  kable(booktabs=TRUE)

ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
wrap_plots(ce_bmtd3)

@@

e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e3_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
